### 2020-06-05 5_evaluation.tex
reduce spaces
Revert "Define METTS."
This reverts commit 8f71ba6a8c85b0e2cefe46a815aa459134ae66c9.

Table~\ref{tab:metg-predict-strong} expands this comparison to the 4
patterns tested in Figure~\ref{fig:metg-compute} for all 11
programming systems that scale well enough to evaluate the separation
between the limit-ideal and limit-actual intersections. We see that
overall, the mean separation is less than $2.15\times$ in node count
and less than $1.31\times$ in time to solution, making this an
accurate way to predict strong scaling in 4 patterns we tested in
Section~\ref{subsec:scalability}.

>>>>

Table~\ref{tab:metg-predict-strong} expands this comparison to the 4
patterns tested in Section~\ref{subsec:scalability} for all 11
programming systems that scale well enough to evaluate the separation
between the limit-ideal and limit-actual intersections. We see that
overall, the mean separation is at most $2.15\times$ in node count
and at most $1.31\times$ in time to solution, making this an
accurate way to predict strong scaling in the 4 patterns we tested in
Section~\ref{subsec:scalability}.

### 2020-06-05 e11_metg_predict_strong.tex
Revert "Define METTS."
This reverts commit 8f71ba6a8c85b0e2cefe46a815aa459134ae66c9.

\vspace{-0.20cm}
\caption{\color{blue} Average factor of separation between METTS-ideal and METTS-actual intersection across the 4 patterns tested in Section~\ref{subsec:scalability}.\label{tab:metg-predict-strong}}
\vspace{-0.5cm}
\end{table}

>>>>

\vspace{-0.20cm}
\caption{\color{blue} Average factor of separation between limit-ideal and limit-actual intersection across the 4 patterns tested in Section~\ref{subsec:scalability}.\label{tab:metg-predict-strong}}
\vspace{-0.5cm}
\end{table}
